---
title: "Statistical Inference Simulation Project"
By: Alysandra Toh
---
Remember to convert to PDF after completion

###Overview:
To investigate the relationship between the exponential distribution in R and the Central Limit Theorom (CLT). There are 3 tasks: 
1. Show the sample mean and compare it to the theoretical mean of the distribution.
2. Show how variable the sample is (via variance) and compare it to the theoretical variance of the distribution.
3. Show that the distribution is approximately normal.
Which I hope to answer in order.

First, to provide reproducibility for the random variables used. Then we set the base characteristics that was provided by the project guideline.

```{r, intro}
set.seed(16)

lambda <- 0.2
sd=mean=1/lambda
n<-40
nosims<-1000
data=rexp(n*nosims, lambda)

```

To simulate rexp(n, lambda) 1000 times, we will keep the data in a neat matrix.
Then, to answer the first question, we will find the sample mean of this simulation and compare it with the theoretical mean (1/lambda).

```{r,cal1}
exD<- matrix(data,nrow=nosims)
exDmean<-apply(exD,1,mean)

##The sample mean of the simulated mean will be:
mean(exDmean)

##while the theoretical mean is 1 over lambda, which is:
print(mean)
```
To show it graphically, we will use a histogram, where the green dotted line is the simulated mean and  the blue is the theoretical. They are almost on top of each other and might be a bit difficult to see separately, which is why I plotted the dotted line on top of the blue one.

```{r, echo=T}
hist(exDmean, xlab="Mean", main="Histogram of Simulated Exponential Means", col="grey"
     )
legend("topright", c("Simulated Mean", "Theoretical Mean"), text.col=c("green", "blue"))
abline(v=mean, col="blue", lwd=2)
abline(v=mean(exDmean),col="green", lty=2)
```
